```{r}
#| output: false
#| echo: false

# Only edit below this line
#############################################################################
test_number <- 16

#Postition of Needle Valve O2 IGN
valve_O2_pos <- 0.5    #Turns from close

#Postition of Neelde valve PRDT
valve_prdt_pos <- 0.1  #Turns from close
#############################################################################
# Only edit above this line
```

---
title: "Pre-Detonator Test"
subtitle: "Test ID `r test_number`"
date: 05.10.2024 
author:
  - name: PERSEUS
    #orcid: 0009-0003-8702-2700
    email: nbartzsch@ethz.ch
    affiliation: 
      - name: ARIS
        url: https://aris-space.ch
editor: visual
format: 
  pdf:
    output-file: "results_test.pdf"
    documentclass: scrartcl
    geometry:
      - left=30mm
      - right=30mm
      - bottom=5mm
      - top=1mm
execute:
  eval: true
  echo: false
---

```{r}
#| output: false

##Load libraries

library(tidyverse)
library(gt)
```

```{r}
#| output: false
#| echo: false

# Only edit below this line
#############################################################################
# Import data
processed_data_sens <- read_csv(file = "processed_data/processed_data_sens.csv")
processed_data_act <- read_csv(file = "processed_data/processed_data_act.csv")

#############################################################################
# Only edit above this line

test_id <- test_number + 1
```

# Test Parameters

```{r}

table_geom <- data.frame(
  O2_pos = paste(valve_O2_pos, "[T.f.c]"),
  prdt_pos = paste(valve_prdt_pos, "[T.f.c]")
)

table_geom |> 
  gt() |> 
  cols_label(
    O2_pos = ("Position of Needle Valve O2 IGN"), 
    prdt_pos = ("Position of Needle Valve PRDT")
  ) |> 
  cols_align(align = "center")
```

# Max Pressure Values

```{r}

actuation_number_open <- (2*test_id)-1
actuation_number_close <- 2*test_id

actuation_time_open <- as.numeric(processed_data_act[actuation_number_open, 1])
actuation_time_close <-  as.numeric(processed_data_act[actuation_number_close, 1])

actuation_time_before <- actuation_time_open - 0.5
actuation_time_after <- actuation_time_close + 1

plot_data <-  processed_data_sens |>
  filter(zero_time > actuation_time_before) |>
  filter(zero_time < actuation_time_after)

plot_data$zero_time <- plot_data$zero_time - actuation_time_open
plot_data$sensor_id <- as.factor(plot_data$sensor_id)
actuation_time_close_relative <-  actuation_time_close - actuation_time_open

processed_data_prdt <- plot_data |>
  filter(sensor_id == 105)

processed_data_ign_ox <- plot_data |>
  filter(sensor_id == 108)

max_prdt_p <- max(processed_data_prdt$value)
max_ign_ox_p <-  max(processed_data_ign_ox$value)

table_max_p <-  data.frame(
  prdt_p = paste(round(max_prdt_p, 2), "[barg]"),
  ign_p = paste(round(max_ign_ox_p, 2), "[barg]")
)

table_max_p |> 
  gt() |> 
  cols_label(
    prdt_p = ("Max Pressure in PRDT"), 
    ign_p = ("Max Pressure in Ign Ox.")
  ) |> 
  cols_align(align = "center")
```

# Plot results

The following plot shows the recorded pressure over time of both the PRDT pressure sensor and the ignition oxidizer pressure. The open state of the valve is marked by the grey box and it opens at t = 0.

```{r, fig.width=10, fig.height=6}

new_labels <- c(
  "105" = "PRDT Pressure",
  "108" = "Ignition Ox. Pressure"
)

ggplot(plot_data, aes(x = zero_time, 
                      y = value, 
                      color = sensor_id)) +
  geom_rect(aes(xmin = 0, xmax = actuation_time_close_relative, ymin = -Inf, ymax = Inf), 
            fill = "#F0F0F0", color = NA, alpha = 0.3) +
  geom_path(linewidth = 0.75)+
  facet_wrap(~ sensor_id, 
             ncol = 1,
             labeller = as_labeller(new_labels), 
             scales = "free") +
  labs(
    x = "Time [seconds]",  
    y = "Pressure [barg]", 
    color = "Pressure reading"
  ) +
  scale_color_manual(values = c("#ff0019", "#001e5e"), labels = new_labels) +
  theme_minimal()
```
